Probabilistic Multiclass Kernel Embedding Classifier

### 2017-04-16 kernel_embedding_classifier.tex
Clear up some contributions

	- Currently, most classification algorithms are binary classifiers, which focuses on the case where the target label can only come from one of two classes.

	- Examples include ...

	- However, many applications require multiclass classifiers

	- Examples include ...

	- Most solve this by doing OVA, AVA, or decision trees on binary classifiers \citep{aly2005survey}

	- Furthermore, those probabilities are usually artificial, by passing through a link function that may or may not be valid, and in many cases like the GPC, is not analytically tractible and requires further approximations. No convergence gaurantees of convergence to the actual decision probabilities

@@

	\begin{itemize}
		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions with convergence guarantees.
		\item A novel hyperparameter training algorithm based on gradient descent and, most importantly, stochastic gradient descent. Reducing the complexity of KEC training from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ for a training dataset of size $n$ and a batch size of $n_{b} << n$. 
		\item Two techniques to estimate the information entropy of a classification prediction with convergence guarantees
		\item Mode reconstruction of the inputs, where we compute the most representative example of each class
	\end{itemize}

@@

\section{Full Probabilistic Inference and Mode Representation Reconstruction}
\label{sec:mode_reconstruction}

@@

>>>>

	\note{Note: Introduction will need a thorough discussion of related work.}

	- Currently, most classification algorithms are binary classifiers, which focuses on the case where the target label can only come from one of two classes. Examples include ...

	- However, many applications require multiclass classifiers. Examples include ...

	- Most solve this by doing binary relevance, such as OVA, AVA, or decision trees on binary classifiers \citep{aly2005survey}

	- Furthermore, those probabilities are usually artificial, by passing through a link function that may or may not be valid, and in many cases like the GPC, is not analytically tractible and requires further approximations. No convergence gaurantees of convergence to the actual decision probabilities.

	- SVMs also are binary by nature. They also do not provide probabilities.

@@

	\begin{itemize}
		\item A novel probabilistic multiclass classifier, the kernel embedding classifier (KEC), based on the theory and framework of kernel embedding of conditional distributions with convergence guarantees on probability and entropy estimates.
		\item A novel training algorithm based on minimising the Rademacher complexity of our kernel embedding classifier in the reproducing kernel Hilbert space, which provides greater generalisation capabilities to the classifier.
		\item A mini-batch stochastic gradient descent variant of the above training algorithm, reducing training complexity from $O(n^{3})$ to $O(n_{b}^{3})$ in time and from $O(n^{2})$ to $O(n_{b}^{2})$ in space for a training dataset of size $n$ and a mini-batch size of $n_{b} << n$.
		\item The application of such a training scheme to learn a deep kernel embedding network and deep convolutional kernel embedding network for image recognition tasks.
		\item Probabilistic inference and mode reconstruction of the inputs, where we quantify and obtain the most representative sample of each class, amongst other statistics.
		\item Probabilistic inference and mode reconstruction on hidden layers of the deep kernel embedding network.
	\end{itemize}

@@

\section{Full Probabilistic Inference and Mode Reconstruction}
\label{sec:mode_reconstruction}

@@

	\note{Note: Not completed yet.}

	\subsection{Hidden Representation Reconstruction}

		\note{Note: Observed quantities are done, but hidden quantities needs experimental verification.}
